---
title: "Final_EDA"
author: "Emily Ferry"
date: "2/24/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(plotly)
library(gapminder)
library(ggthemes)
library(dplyr)
library(tidyr)
library(ISLR)
library(leaflet)
library(data.table)
library(RColorBrewer)
library(tsdl)
library(forecast)
req.packages<-c("leaflet","tidycensus","tidyverse","ggthemes","ggExtra","scales")


```

data

```{r cars}

#load data here 

##avocado 
rm(list=ls())
avocado<- fread("avocado.csv", header = TRUE, data.table = FALSE) 
#str(avocado)

#changing date character to a date 
avocado <- avocado %>%
  mutate(date = as.Date(Date, format = "%m/%d/%y"))
# convert year to factor
avocado$year <- as.factor(avocado$year)

# Taking a look at the TotalVolume column
avocado$totalsales <- avocado$totalsales - avocado$TotalBags

avocado <- avocado %>% 
  rename(SmallHass = `4046`, LargeHass = `4225`, XLargeHass = `4770`, TotalVolume = totalsales)%>%
  gather(AvocadoSize, AvocadoVolume, c(SmallHass, LargeHass, XLargeHass))%>%
  gather(BagsSize, TotalBags, c(SmallBags, LargeBags, XLargeBags))



# Arranging by Date column       
avocado <- arrange(avocado, Date)

avocado %>% sample_n(1000)

#looking at region
avocado_region <- avocado %>% filter(region %in% c("California", "GreatLakes", "Midsouth", "Northeast", "Plains", "SouthCentral", "Southeast",  "West"))

avocado%>% sample_n(1000)


# subsetting data by Total US
avocado_totalUS <- avocado %>% filter(region == "TotalUS")
avocado_totalUS %>% sample_n(936)
gc()

```


### The Data 

```{r}
DT::datatable(avocado, options = list(
  pageLength = 25
))
```


  This Data set contains Historical Data on avocado prices and sales volume accross multiple U.S. makets. The dataset was found on Kaggle, while the data originates from the HASS Avocado Board (https://hassavocadoboard.com). 

  In recent years, avocado sales have taken off (thanks to Millenials... I myself consumed three avocados in the week and a half I worked on this dashboard...). In fact, with some clever marketing of Guacamole during the NFL, avocados have certainly had their time to shine, By looking at historical sales of produce we can hope to realize some of the following: 
  
  -Future demand of a certain product category (ie. small vs. large avocados or organic vs. convential produce)
  -Future Pricing 
  -Potential growth markets
  -Better informed Marketing Strategies 

In the following analysis I will look to find the most popular avocado type based on historical sales(size,type), the average avocado price that generate the most sales volume and the region that has historically consumed the most avocados to date. 



Organic vs conventional (Plotly)
```{r}

options(scipen = 1000000)
  
plot1<- avocado %>% 
  sample_n(1000) %>% 
  ggplot(data = ., aes(x = AveragePrice, y = TotalVolume, color = type))+
      geom_point()+
      labs(x = "Average Avocado Price", y = "Total Sales", title = "Total Sales Volume by Average Avocado Price", subtitle = "Organic Vs. Conventional", caption = "Kaggle:Avocado Dataset")+
  scale_y_continuous(labels = scales::dollar)+
  theme_minimal() +
  scale_color_manual(values=c("#CCFF66","#333300"))

ggplotly(plot1)
       
```

avocado sales by region 
```{r}

avocado_region %>%
  ggplot(aes(x = reorder(region, -AvocadoVolume), y = AvocadoVolume/1000000, fill = AvocadoSize)) +
  geom_col(position = "stack") +
  theme_minimal() +
  labs(x = "Region", y = "Total Volume (in Milions)") +
  scale_fill_manual(values = c("#FFFF99","#CCFF66" ,"#333300"), name = "Avocado Size") +
  ggtitle("Regional Single Avocado Sales")


```

Avocado sales by region
```{r}
avocado_region %>% 
  filter(type == "conventional") %>%
  ggplot(aes(x = date, y = TotalVolume,color = region)) +
  #geom_line(size = 0.75) +
  labs(x = "Date", y = "Total Sales", title = "Total Sales By Region", subtitle = "Line Plot") +
  theme_light() +
  theme(panel.border = element_rect(color = "grey35")) +
  scale_y_continuous(labels = scales::dollar) +
  geom_smooth(aes(y = TotalVolume), se = F, span = 0.4)
  
```







#forecasting:honestly this was alot - sort of gave up on this notion 

```{r}
avocado_totalUS

ts(avocado$TotalVolume,
   start = c(2015,1), frequency = 12)->ts_avo

plot(ts_avo)


ts_avo%>% forecast(level= c(80,95))->dum2
plot(dum2)


```



