---
title: "Avocado Sales Data"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
runtime: shiny 
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(ggthemes)
library(shiny)
library(plotly)
library(knitr)
library(data.table)
library(tseries)
library(forecast)
library(dplyr)

```


```{r avo data, include=FALSE, warning=FALSE}
#load data here 

##avocado 
rm(list=ls())
avocado<- fread("avocado.csv", header = TRUE, data.table = FALSE) 
#str(avocado)

#changing date character to a date 
avocado <- avocado %>%
  mutate(date = as.Date(Date, format = "%m/%d/%y"))
# convert year to factor
avocado$year <- as.factor(avocado$year)

# Taking a look at the TotalVolume column
avocado$totalsales <- avocado$totalsales - avocado$TotalBags

avocado <- avocado %>% 
  rename(SmallHass = `4046`, LargeHass = `4225`, XLargeHass = `4770`, TotalVolume = totalsales)%>%
  gather(AvocadoSize, AvocadoVolume, c(SmallHass, LargeHass, XLargeHass))%>%
  gather(BagsSize, TotalBags, c(SmallBags, LargeBags, XLargeBags))



# Arranging by Date column       
avocado <- arrange(avocado, Date)

avocado %>% sample_n(1000)

#looking at region
avocado_region <- avocado %>% filter(region %in% c("California", "GreatLakes", "Midsouth", "Northeast", "Plains", "SouthCentral", "Southeast",  "West"))

avocado%>% sample_n(1000)


# subsetting data by Total US
avocado_totalUS <- avocado %>% filter(region == "TotalUS")
avocado_totalUS %>% sample_n(936)
gc()

```

Overview of the Data 
==============================

Row {data-width=650}
---------------------------------------
### Organic Vs. Conventional Avocado Sales 

```{r}
renderPlotly({
  
options(scipen = 1000000)
  
plot1<- avocado %>% 
  sample_n(1000) %>% 
  ggplot(data = ., aes(x = AveragePrice, y = TotalVolume, color = type))+
      geom_point()+
      labs(x = "Average Avocado Price", y = "Total Sales", title = "Total Sales Volume by Average Avocado Price", subtitle = "Organic Vs. Conventional", caption = "Kaggle:Avocado Dataset")+
  scale_y_continuous(labels = scales::dollar)+
  theme_minimal() +
  scale_color_manual(values=c("#CCFF66","#333300"))

ggplotly(plot1)

})

```


### The Data 

```{r}
DT::datatable(avocado_totalUS, options = list(
  pageLength = 25
))
```


Row {data-width=350}
-----------------------------------

  This Data set contains Historical Data on avocado prices and sales volume accross multiple U.S. makets. The dataset was found on Kaggle, while the data originates from the HASS Avocado Board (https://hassavocadoboard.com). 
  In recent years, avocado sales have taken off (thanks to Millenials... I myself consumed three avocados in the week and a half I worked on this dashboard...). In fact, with some clever marketing of Guacamole during the NFL, avocados have certainly had their time to shine, By looking at historical sales of produce we can hope to realize some of the following: 
  -Future demand of a certain product category (ie. small vs. large avocados or organic vs. convential produce)
  -Future Pricing 
  -Potential growth markets
  -Better informed Marketing Strategies 
  In the following analysis I will look to find the most popular avocado type based on historical sales(size,type), the average avocado price that generate the most sales volume and the region that has historically consumed the most avocados to date. 



### Avocado Sales by Size of Avocado
=====================================

Inputs {.sidebar}
-------------------------------------------

```{r}
inputPanel(
  selectInput(inputId = "AvocadoSize1",
              label = "Avocado Size",
              choices = unique(avocado$AvocadoSize),
              multiple = FALSE)
           )
```

```{r}
renderPlot({
  
 avocado_region %>%
     dplyr::filter(AvocadoSize1 %in% input$AvocadoSize1)%>%
  ggplot(aes(x = reorder(region, -AvocadoVolume), y = AvocadoVolume/1000000, fill = AvocadoSize)) +
  geom_col(position = "stack") +
  theme_minimal() +
   labs(x = "Region", y = "Total Volume (in Milions)") +
   scale_fill_manual(values = c("#FFFF99","#CCFF66" ,"#333300"), name = "Avocado Size") +
   ggtitle("Regional Hass Sales")
           
})

```

South Central is the higest purchaser of conventional Hass and small Hass while the Northeast purchase the most large Hass. In comparison to small and large Hass, there is not a high volume of extra large Hass purchases.

### Regional Avocado Sales
====================================

Inputs {.sidebar}
-------------------------------------------

```{r}
inputPanel(
  selectInput(inputId = "Region",
              label = "Regional Sales",
              choices = unique(avocado_region$region),
              multiple = TRUE)
           )
```

```{r}
renderPlot({
  
avocado_region %>% 
    dplyr::filter(Region == input$Region)%>%
   filter(type == "conventional") %>%
  ggplot(aes(x = date, y = TotalVolume,color = region)) +
  #geom_line(size = 0.75) +
  labs(x = "Date", y = "Total Sales", title = "Total Sales By Region", subtitle = "Line Plot")+
  theme_minimal() +
  theme(panel.border = element_rect(color = "grey35")) +
  scale_y_continuous(labels = scales::dollar) +
  geom_smooth(aes(y = TotalVolume), se = F, span = 0.4)
})
  
```



